Beam Helicity and Charge Asymmetries in the Bethe-Heitler and Deeply-Virtual Compton Scattering Processes on an Unpol Proton Target \\ \underline{Paper Tag: dvcsP0607} \hspace*{1cm}\underline{Drafting Committee: 90}

### 2011-11-21 results_dual.tex

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of figure~\ref{bsa_xbjrange}. Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.

The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in figure~\ref{bca_xbjrange}. The systematic uncertainties are estimated in the same procedure as used to estimate the systematic uncertainties of the beam-helicity asymmetries. The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero. There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as they depend on the same $\mathcal{C}$-function. The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regards to $A_{\textrm{C}}^{\cos\phi}$ can be found in table~\ref{tab_amplitudes}. The measured amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ but they have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$. The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs. Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading-twist amplitudes.

@@

The dash-dotted curves in figure~\ref{bsa_xbjrange} shows the result of a calculation from a fit based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}. The ``Regge'' term is extended to include contributions that determine the $t$-dependence of the corresponding GPD. The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and DVCS data from Jefferson Laboratory (to describe the skewness dependence). The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude reported here well, but the projections in the other kinematic variables are not as well described.

>>>>

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}. The leading twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of figure~\ref{bsa_xbjrange}. Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.

The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in figure~\ref{bca_xbjrange}. The systematic uncertainties are estimated in the same procedure as used to estimate the systematic uncertainties of the beam-helicity asymmetries. The leading twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero. There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as they depend on the same $\mathcal{C}$-function. The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regards to $A_{\textrm{C}}^{\cos\phi}$ can be found in table~\ref{tab_amplitudes}. The measured amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ but they have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$. The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs. Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading twist amplitudes.

@@

The dash-dotted curves in figure~\ref{bsa_xbjrange} shows the result of a calculation from a fit based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}. The ``Regge'' term is extended to include contributions that determine the $t$-dependence of the corresponding GPD. The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and DVCS data from Jefferson Laboratory (to describe the skewness dependence). The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude reported here well, but the projections in the other kinematic variables are not as well described. The model describes the trends of the $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes well.
